An open reproducible framework for the study of the iterated prisoner's dilemma

### 2016-06-02 tex/response.tex

\documentclass{jors}

%% Set the header information

% Commenting out as this overrides the section titles.
\pagestyle{fancy}
\definecolor{mygray}{gray}{0.6}
\renewcommand\headrule{}
\rhead{\footnotesize 3}
\rhead{\textcolor{gray}{UP JORS software Latex paper template version 0.1}}

% Nicer bibliography management
\usepackage[backend=bibtex, firstinits=true, url=true, isbn=true]{biblatex}
\addbibresource{references.bib}
%-----------------------------

\usepackage{amsmath}  % Basic
\usepackage{booktabs}  % Better tables
\usepackage{graphicx}  % Images
\usepackage{hyperref}  % Links etc
% \usepackage{minted}  % Code: minted does not compile on arXiv
\usepackage{multicol}  % Multi column list
\usepackage{subcaption}  % Subfigures

\begin{document}
%% Set the header information
\pagestyle{fancy}
\definecolor{mygray}{gray}{0.6}
\renewcommand\headrule{}
\rhead{\footnotesize 3}
\rhead{\textcolor{gray}{UP JORS software Latex paper template version 0.1}}

\rule{\textwidth}{1pt}

\section*{(1) Overview}\label{sec:sec:overview}

\vspace{0.5cm}

\section*{Title}

Response to first review: An open framework for the reproducible study of the
iterated prisoner's dilemma.

\section*{Major comments}

\begin{itemize}
\item \textit{suggested title change}: This has been changed to ``An open framework for
      the reproducible study of the iterated prisoner's dilemma''
\item Implementation & Architecture section currently discusses how to use library, but should be refactored to expand upon architecture
\item \textit{Side-by-side figures appear too small, and should be replaced with full-size (perhaps top-bottom) figures}: Figures have been resized.
\item Discrepancy between version of software in paper and on Zenodo
\item \textif{Dependencies not automatically installed or checked via pip}: This has been addressed. Here is a url to the code patch (github pull request) that fixed this: \url{https://github.com/Axelrod-Python/Axelrod/pull/542}.
\end{itemize}

\section*{Minor comments}

Documentation paragraph in the prob end tournament section has been fixed. It now reads:

\begin{quote}
	We can also view the length of the matches played by each player. The plot
	shows that the length of each match (for each player) is not the same. The
	median length is 4 which is the expected value with the probability of a match
	ending being 0.5.
\end{quote}

The code snippets that were not complete (final line for plotting) have been
fixed. Furthermore, an explanation of how to obtain the full tournament results
has also been included.

The comment about variety of backgrounds: we feel that the paragraph explains what is meant (

The discussion group has been made public. This was an oversight.

Hypothesis is a requirement for development: cloudpickle is no longer a
requirement following some substanstial rewriting of the internals of the
library (resulting in speed, memory and readability improvements).

\end{document}

### 2016-06-03 tex/paper.tex
Minor details: update.
- Number of strategies
- Coverage percentage

\begin{itemize}[noitemsep,topsep=0pt]
    \item Open: all code is released under an MIT license;
    \item Reproducible and well-tested: at the time of writing there is an excellent level of
        integrated tests with 99.37\% coverage (including property based tests:
        \cite{Hypothesis3.0.3})
    \item Well-documented: all features of the library are documented for ease of
        use and modification
    \item Extensive: 123 strategies are included, with infinitely-many
        strategies available in the case of parametrised strategies
    \item Extensible: easy to modify to include new strategies and to run new tournaments
\end{itemize}

>>>>

\begin{itemize}[noitemsep,topsep=0pt]
    \item Open: all code is released under an MIT license;
    \item Reproducible and well-tested: at the time of writing there is an excellent level of
        integrated tests with 99.73\% coverage (including property based tests:
        \cite{Hypothesis3.0.3})
    \item Well-documented: all features of the library are documented for ease of
        use and modification
    \item Extensive: 135 strategies are included, with infinitely-many
        available in the case of parametrised strategies
    \item Extensible: easy to modify to include new strategies and to run new tournaments
\end{itemize}
